### 2013-01-29 Docs/Thesis/background.tex
Clarify definition of signal functions in background.

An alternative approach to FRP was first proposed in work on
Fruit~\cite{Courtney2001-1}, a library for declarative specification of GUIs.
This library utilized the concept of Arrows~\cite{Hughes2000} as an abstraction
for {\em signal functions}. Arrows are abstract type constructors with input and
output type parameters, together with a set of routing combinators (see Figure~\ref{figure:arrow_combinators}).
Signal functions form an arrow. Signal functions represent time-dependent and
reactive transformers of events and signals. Signals and events
cannot be directly manipulated by the programmer. This approach has two
motivations: it increases modularity since both the input and output of signal
functions may be transformed (as opposed to signals or events which may only be
transformed in their output) and it avoids a large class of time and space leaks
which have emerged when implementing FRP with first-class signals and events.

>>>>

An alternative approach to FRP was first proposed in work on
Fruit~\cite{Courtney2001-1}, a library for declarative specification of GUIs.
This library utilized the concept of Arrows~\cite{Hughes2000} as an abstraction
for {\em signal functions}. Arrows are abstract type constructors with input and
output type parameters, together with a set of routing combinators (see
Figure~\ref{figure:arrow_combinators}). The concept of an Arrow in Haskell,
including the axioms the combinators of an arrow must satisfy, are derived from
the concept of arrows from category theory.

Signal functions are time-dependent and reactive transformers of events and
signals. Signals and events cannot be directly manipulated by the programmer.
This approach has two motivations: it increases modularity since both the input
and output of signal functions may be transformed (as opposed to signals or
events which may only be transformed in their output) and it avoids a large
class of time and space leaks which have emerged when implementing FRP with
first-class signals and events.
